\documentclass[nopalatino,nolot,nolof,color]{fithesis3}
\thesissetup{
 faculty=fi,
 type=mgr,
 author={Bc. Václav Dedík},
 advisor={Bruno Rossi, PhD},
 title={Automatic Ticket Triage Using Supervised Text Classification},
 keywords={Bug, Ticket, Machine Learning, Text Classification, Assignee, Triage},
 abstract={Software projects typically use an issue tracking system to which both users and developers report bugs. The challenge is to correctly assign developers to these bug reports in order to resolve the issues as fast as possible. With the advent of machine learning and text classification algorithms, new automatic approaches that address this concern were proposed. In this thesis, we evaluate these approaches both on open source and proprietary datasets. Furthermore, we run analysis on the datasets to determine if they are significantly different and if the time aspect of the datasets affects the performance of our classification models. Finally, the results are discussed and compared in detail.},
 autoLayout=false}
\usepackage{lmodern}
\usepackage{lipsum}
\usepackage{todo}
\usepackage{hyperref}
\usepackage{framed}
\usepackage{pdflscape}
\usepackage{tikz}
\usepackage{amsmath}
\usetikzlibrary{trees}
\usepackage[
    type={CC},
    modifier={by},
    version={4.0},
]{doclicense}
\renewcommand{\todomark}{}

\DeclareMathOperator*{\argmax}{arg\,max}
\newtheorem{theorem}{Theorem}

\begin{document}
 \makeatletter
  \thesis@blocks@cover
  \thesis@blocks@titlePage
  \thesis@blocks@frontMatter
  \begin{center}
    \begin{minipage}{\textwidth}
      This thesis is licensed under a \doclicenseLongNameRef~license \doclicenseIcon.%
    \end{minipage}
  \end{center}
  \thesis@blocks@assignment
  \thesis@blocks@declaration
  \thesis@blocks@thanks
  \thesis@blocks@clearRight
  \thesis@blocks@abstract
  \thesis@blocks@keywords
  \thesis@blocks@tables
  \thesis@blocks@mainMatter
 \makeatother

 \input{chapters/Introduction}
 \input{chapters/Related_Work}
 \input{chapters/Background}
 \input{chapters/Methodology}
 \input{chapters/Evaluation}
 \input{chapters/Discussions}
 \input{chapters/Conclusion}

 \bibliographystyle{IEEEtran}
 \bibliography{thesis}

 \appendix
 \chapter{Links}

 \section{GitHub Repositories}

 This section contains links to GitHub repositories created while working on this thesis. First link contains source code of the thesis text. Second link contains the source code of a web application that was created for the company that provided the proprietary dataset. The last link contains the source code of a Python library based on numpy, scikit-learn and scipy created for better usage of several ML models and feature extraction techniques.

 \begin{itemize}
   \item[Thesis text]: \url{https://github.com/VaclavDedik/masters-thesis}
   \item[Triager]: \url{https://github.com/VaclavDedik/triager}
   \item[Classifier]: \url{https://github.com/VaclavDedik/classifier}
 \end{itemize}

 \todos
\end{document}